Human-level control through deep reinforcement learning

### 2018-01-01 article/article.tex

@@

%\newpage
\footnotesize
\bibliographystyle{apalike}
\bibliography{article}

>>>>

Figure~\ref{fig:t-SNE}\todo{Link the right figure} shows a 2-dimensional representation of the last fully connected hidden layer, i.e. a 512-dimensional
vector. The method of \textit{projection} that was used is t-SNE~\citep{maaten2008visualizing}, which is part of the manifold learning algorithms, also
called \textit{Nonlinear Dimensionality Reduction}~\citep{lee2007nonlinear}.

The implementation of t-SNE that was used is the one from Scikit-Learn~\citep{scikit-learn}, the Python library.

@@

\newpage
\footnotesize
\bibliographystyle{apalike}
\bibliography{article}
